Modelling last glacial cycle ice dynamics in the Alps

### 2017-01-18 articles/cycle/alps-cycle.tex
Update outline to Nature format and new abstract.
Add selected figures into manuscript.
Nature format is limited to four figures. I have many more... Can't quite
settle on which to include.

* 21 ka snapshot -> for sure
* Timing of the LGM -> for sure
* Trimlines -> harder to understand, easier to critic
* Erosion -> slightly off-topic, but interesting to many

Maybe another figure clearly showing the many glacier advances, like the Rhine
profile or an improved number of glaciations map, is still needed. I guess I
should work and see if I can improve these two.

\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}

@@

\section{Introduction}

\section{Model set-up}
\subsection{Overview}
\subsection{Ice rheology}
\subsection{Basal sliding}
\subsection{Bedrock deformation}
\subsection{Surface mass balance}
\subsection{Climate forcing}
    Fig. -- GRIP and EPICA time series
\subsection{Computing cost}
    Fig. -- Scalability
    Fig. -- Time stamps

\section{Results}
\subsection{Ice cap evolution}
    Fig. -- 21 ka snapshot and time series
\subsection{Ice thickness}
    Fig. -- Trimlines
\subsection{Timing of the LGM}
    Fig. -- Timing of the LGM
\subsection{Total sliding}
    Fig. -- Total sliding
\subsection{Uplift rates}
    Fig. -- Uplift rates

@@

>>>>

\usepackage{authblk}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[pdftex]{xcolor}
\usepackage[pdftex]{graphicx}
\graphicspath{{../../figures/}}

@@

\section{Main}
\subsection{Introduction}
\subsection{Ice cap evolution}
    Fig.~\ref{fig:lgmvel} -- Snapshot at 21\,ka and volume time series.
\subsection{Timing of the LGM}
    Fig.~\ref{fig:timing} -- Timing of the LGM and area time series.
\subsection{Ice thickness}
    Fig.~\ref{fig:trimlines} -- Ice thickness comparison to trimlines.
\subsection{Erosion potential}
    Fig.~\ref{fig:erosion} -- Integrated erosion potential.

\section{Methods}
\subsection{Overview}
    Tab. -- Model parameters
\subsection{Ice rheology}
\subsection{Basal sliding}
\subsection{Bedrock deformation}
\subsection{Surface mass balance}
\subsection{Climate forcing}
    Fig.~\ref{fig:inputs} -- Climate and geothermal model inputs.\\
    Tab. -- Records\\
    Fig.~\ref{fig:timeseries} -- Low-resolution time series.\\
    Fig.~\ref{fig:footprints} -- Low-resolution ice cover.

@@

% ----------------------------------------------------------------------
% References
% ----------------------------------------------------------------------

\bibliographystyle{abbrvnat}
\bibliography{../../references/references}

% ----------------------------------------------------------------------
% Figures
% ----------------------------------------------------------------------

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_lgmvel}}
      \caption{Model output at 21\,ka.}
      \label{fig:lgmvel}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_timing}}
      \caption{Timing of the LGM and area time series.}
      \label{fig:timing}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_trimlines}}
      \caption{Ice thickness comparison to trimlines.}
      \label{fig:trimlines}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_erosion}}
      \caption{Integrated erosion potential.}
      \label{fig:erosion}
    \end{figure}

% ----------------------------------------------------------------------
% Supplementary tables
\setcounter{table}{0}
\renewcommand{\thetable}{S\arabic{table}}%
% ----------------------------------------------------------------------

% ----------------------------------------------------------------------
% Supplementary figures
\setcounter{figure}{0}
\renewcommand{\thefigure}{S\arabic{figure}}%
% ----------------------------------------------------------------------

    \begin{figure}
      \centerline{\includegraphics{alpcyc_hr_inputs}}
      \caption{Climate and geothermal model inputs.}
      \label{fig:inputs}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_lr_timeseries}}
      \caption{Low-resolution time series.}
      \label{fig:timeseries}
    \end{figure}

    \begin{figure}
      \centerline{\includegraphics{alpcyc_lr_footprints}}
      \caption{Low-resolution ice cover.}
      \label{fig:footprints}
    \end{figure}
